An Architecture for Real-Time Location Recommendation for Field Data Collection

### 2017-03-30 Dynamic Enumerator Allocation/Paper/v3.a/Paper.tex
Update paper

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Field data collection is one of the main activities performed by the national statistical agencies in every country. Data collection activities have a similiar workflow with Multi Depot Vehicle Routing Problem (MDVRP). The use of MDVRP to generate pre-calculated routes resulted in a total route costs with high standard deviation. Real-time mechanism by utilizing the publish/subscribe paradigm combined with Cooperative Coevolution Algorithms (CoEAs) is proposed to reduce the inequality (large variation) of the completion time. The test results show that the routes produced by publish/subscribe paradigm combined with CoEAs are more prevalent in total route times among enumerators compared with pre-calculated routes produced by only CoEAs.
\end{abstract}

@@

%-----------------------------------------------------------------------------%
\section{Introduction}
\label{sec:introduction}
%-----------------------------------------------------------------------------%
Data collection is one of the main duties of the statistical agency in every country, including BPS-Statitics Indonesia. There are two data collection methods that are generally used: primary data collection and secondary data collection. In the primary data collection, the enumerators directly meet and interview the respondents, while in the secondary data collection, the statistical institution only compiles the data collected by other agencies. The primary data collection method requires the enumerators to be allocated to several census/survey areas that have been specified before. The allocation is usually made by assigning an equal number of locations on each enumerator.

The workflow of the data collection performs as follows: 
\begin{enumerate}
	\item The enumeration will start on a particular point. It could be the statistical office or the enumerator's house. 
	\item The enumerator moves to the first census/survey location and visits all respondents in that location. 
	\item After finishing the first census/survey area, the enumerator moves to the second census/survey location and continue doing so until all locations have been visited successfully.
\end{enumerate}

This workflow is significantly similar to the Vehicle Routing Problem (VRP), or more specifically, the Multi Depot Vehicle Routing Problem (MDVRP).

However, although the data collection shares similar workflow with MDVRP, the rough implementation of the MDVRP algorithm is not feasible to solve the allocation problems. This is because one important variables needed in the algorithm, the service time, is not available until after the enumerator finish visiting the census/survey location. Therefore, this research aims to propose an integration of MDVRP with pub/sub mechanism to create a location recommendation system for field data collection that can be used in real time.

%-----------------------------------------------------------------------------%
\section{Literature Review}
\label{sec:literature-review}
%-----------------------------------------------------------------------------%
%-----------------------------------------------------------------------------%
\subsection{Multi-Depot Vehicle Routing Problem}
\label{ssec:mdvrp}
%-----------------------------------------------------------------------------%
Multi-Depot Vehicle Routing Problem (MDVRP) is one of classic  Vehicle Routing Problem (VRP) variance, where there are more than one depot that can be used  \cite{montoya-torres_literature_2015}. \autoref{fig:mdvrp-illustration} shows an example of the solution for VRP problem that uses two depot and two vehicle routes which associated with each depot. Basically, a solution to this problem is a set of vehicle routes such that: (i) each vehicle route starts and ends at the same depot, (ii) each customer is served exactly once by one vehicle, (iii) the total demand on each route does not exceed vehicle capacity (iv) the maximum route time is satisfied and (v) the total cost is minimized.

\begin{figure}[h]
	\centering
	\includegraphics[width=6cm]{Resources/Images/mdvrp-illustration}
	\caption{An illustration for \textit{Multi Depot} VRP}
	\label{fig:mdvrp-illustration}
\end{figure}

According to Renaud et al \cite{renaud_tabu_1996}, the MDVRP can be formally described as follows. Let $G = (V, A)$ be a complete graph, where $V$ is the set of nodes and $A$ is the set of arcs. The nodes are partitioned into two subsets: the customers to be served, $V_C$ = \{1,..., $N$\}, and the multiple depots $V_D$ = \{$N$+1,..., $N+M$\}, with $V_C \cup V_D$ = $V$ and $V_C \cap V_D$ = $\oslash$. There is a non-negative cost $c_{ij}$ associated with each arc $(i, j) \in A$. The demand of each customer is $d_i$ (there is no demand at the depot nodes). There is also a fleet of $K$ identical vehicles, each with capacity $Q$. The service time at each customer $i$ is $t_i$ while the maximum route duration time is set to $T$. $A$ conversion factor $w_{ij}$ might be needed to transform the cost $c_{ij}$ into time units. In the classical MDVRP, however, the cost is the same as the time and distance units, so $w_{ij}$ = $1$.

In the mathematical formulation \cite{kulkarni_integer_1985}, binary variables $x_{ijk}$ are equal to $1$ when vehicle $k$ visits node $j$ immediately after node $i$. Auxiliary variables $y_i$ are also used in the subtour elimination constraints.

Minimize
\begin{flalign}
\label{eq:1}
\sum_{i=1}^{N+M}\sum_{j=1}^{N+M}\sum_{k=1}^{K}c_{ij}x_{ijk};
\end{flalign}

Subject to:
\begin{flalign}
\label{eq:2}
\sum_{i=1}^{N+M}\sum_{k=1}^{K}x_{ijk} = 1  (j=1,..., N);
\end{flalign}

\begin{flalign}
\label{eq:3}
\sum_{j=1}^{N+M}\sum_{k=1}^{K}x_{ijk} = 1  (j=1,..., N);
\end{flalign}

\begin{flalign}
\label{eq:4}
&\sum_{i=1}^{N+M}x_{ihk} - \sum_{j=1}^{N+M}x_{hjk} = 0 \\
\nonumber
&(k=1,...,K; h=1,...,N+M);
\end{flalign}

\begin{flalign}
\label{eq:5}
\sum_{i=1}^{N+M} \sum_{j=1}^{N+M} d_ix_{ijk} \leq Q (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:6}
\sum_{i=1}^{N+M} \sum_{j=1}^{N+M} (c_{ij}w_{ij} + t_i) x_{ijk} \leq T (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:7}
\sum_{i=N+1}^{N+M} \sum_{j=1}^{N} x_{ijk} \leq 1 (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:8}
\sum_{j=N+1}^{N+M} \sum_{i=1}^{N} x_{ijk} \leq 1 (k=1,...,K);
\end{flalign}

\begin{flalign}
\label{eq:9}
&y_i - y_j + (M + N)x_{ijk} \leq N + M - 1; \\
\nonumber
&for 1 \leq i \neq j \leq N and 1 \leq k \leq K;
\end{flalign}

\begin{flalign}
\label{eq:10}
x_{ijk} \in \{0, 1\} \forall i,j,k;
\end{flalign}

\begin{flalign}
\label{eq:11}
y_i \in \{0,1\} \forall i;
\end{flalign}

The objective \ref{eq:1} minimizes the total cost. Constraints \ref{eq:2} and \ref{eq:3} guarantee that each customer is served by exactly one vehicle. Flow conservation is guaranteed through constraint \ref{eq:4}. Vehicle capacity and route duration constraints are found in \ref{eq:5} and \ref{eq:6}, respectively. Constraints \ref{eq:7} and \ref{eq:8} check vehicle availability. Subtour elimination constraints are in \ref{eq:9}. Finally, \ref{eq:10} and \ref{eq:11} define x and y as binary variables.

%-----------------------------------------------------------------------------%
\subsection{Evolution Algorithms}
\label{ssec:evolution-algorithms}
%-----------------------------------------------------------------------------%
Evolution Algorithms (EAs) is one of the optimization algorithm families that are inspired by nature. In the evolution algorithm, there are selection and reproduction processes to purify the population from the solution candidates. According to Engelbreacht \cite{engelbrecht_coevolution_2007}, in general, the EAs lifecycle begins with randomly configuring the initial population. Afterwards, for each iteration, every individual in the population is evaluated using an objective function. Then, each solution candidate will be labeled with a fitness value based on their evaluation result. These solution candidates will then commit a reproduction and create the next generation. The whole process will be repeated using the new-generation individuals. These iterations will stop once it hits a certain time limit, which is 60 seconds.

Coevolutionary algorithms (CoEAs) is a development of EAs. In standard EAs, evolution is usually viewed as the population attempts to adapt in a fixed physical environment. In contrast, coevolutionary algorithms (CoEAs) realize that in natural evolution the physical environment is influenced by other independently-acting biological populations \cite{engelbrecht_coevolution_2007}. Based on the interaction of each species, CoEAs can be distinguished into two categories: competitive and cooperative \cite{engelbrecht_coevolution_2007}. In the competitive coevolution, each individual competees with other individuals in the same group. Meanwhile, in cooperative coevolution, the interaction between species is mutualistic, or at least, not harming each other.

%-----------------------------------------------------------------------------%
\subsection{Publish/Subscribe Paradigm}
\label{ssec:pub-sub}
%-----------------------------------------------------------------------------%
Publish/subscribe interaction is one of the communication methods between client and server. The interaction paradigm in publish/subscribe is the presence of subscribers that have an interest in a certain event or the pattern of an event. These subscribers will be notified by the publisher about the event they are interested in \cite{eugster_many_2003}.

The basic model of the publish/subscribe system, as can be seen in \autoref{fig:pub-sub-general}, depends on the event notification service that provides storage and management of subscription. This event service acts as a mediator between the publisher, who acts as the events producer, and the subscriber who acts as the event consumer.

\begin{figure}[h]
	\centering
	\includegraphics[width=8cm]{Resources/Images/pub-sub-general}
	\caption{Basic architecture in Pub/Sub \cite{eugster_many_2003}}
	\label{fig:pub-sub-general}
\end{figure}

One of the benefits of publish/subscribe mechanism is the loose coupling characteristic \cite{eugster_many_2003} between the publisher and the subscriber. The separation of information (decoupling) between publisher and subscriber can be divided into 3 (three) dimension, which are:

\begin{enumerate}
	\item Space decoupling. \\
	In doing the interaction, both publisher and subscriber do not need to know each other. The publisher sends an event and subscriber indirectly receive the event through the event service. The publisher does not hold any reference regarding the subscriber and vice versa. 
	\item Time decoupling. \\
	The parties who are involved in the interactions do not have to interact in the same time. The publisher can send the event even though he is in a disconnected state. Similarly, the subscriber can still receive the event, albeit disconnected. 
	\item Synchronizing decoupling. \\
	Publisher will not be blocked when producing the event. The subscriber can still obtain information despite, at the same time, working on other tasks. Publisher and subscriber are not in the main flow, hence are not interacting synchronously. 
\end{enumerate}

%-----------------------------------------------------------------------------%
\section{Proposed Solution}
\label{sec:proposed-solution}
%-----------------------------------------------------------------------------%
The drawback of using MDVRP for location recommendation in field data collection is the absence of time service data, which is very important in the recommendation calculation. Thus, MDVRP needs to be integrated with the real-time mechanism. There are several mechanisms that can be adopted in a real-time system such as Web Service, Remote Procedure Call (RPC), message passing, and publish/service \cite{eugster_many_2003}.

The publish/subscribe mechanism is used in this research because it has the \textit{loose coupling} characteristic. Furthermore, publish/subscribe mechanism is also suitable for an information-driven system \cite{muhl_large-scale_2002}. Because of this characteristic, the publish/subscribe mechanism can work asynchronously, where request and reply do not have to be processed in sequence. The publisher and subscriber can conduct an offline publish and offline subscribe, respectively.

\begin{figure}[h]
	\centering
	\includegraphics[width=8cm]{Resources/Images/system-overview}
	\caption{The system outline}
	\label{fig:system-overview}
\end{figure}

\autoref{fig:system-overview} shows the system outline that consists of 3 (three) main components: the publisher, the subscriber, and the message broker. The communication between publisher and subscriber is built upon a similarity in either event or topic. In this research, the topic that is used as the basis for the communication between publisher and subscriber is the \textit{current location} of each subscriber.

%-----------------------------------------------------------------------------%
\subsection{Recommendation Publisher}
\label{ssec:recommendation-publisher}
%-----------------------------------------------------------------------------%
VRP solver is implemented on the publisher's side, who will search for solution/route and then publish it to the subscriber via the message broker. The subscriber's current location is used as a topic. Afterward, a thread  (\autoref{alg:topic-watcher}) is prepared that will periodically check if there is any new topic at message broker.

Each time a new topic emerge, a new thread will be created and that new topic will be used as an ID for that thread. Each thread contains VRP solver procedure (\autoref{alg:vrp-worker}) that will do the solution/route finding. Accordingly, a threadpool is provided to contain all threads from each topic in order of arrival time. Since topic is used as a thread ID, the threadpool size is equal to the number of census/survey location.

Each thread in thread pool will be run in order, one session for each thread. Every running thread, with a topic as an ID, will find the solution by embroiling all $M$ vehicles and $(unassigned) N$ locations. The solution finding is done using VRP solver procedure which is explained in more detail in \autoref{ssec:vrp-solver}.

\begin{algorithm}[h]
	\caption{TopicWatcher}
	\label{alg:topic-watcher}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE $C$
		\ENSURE  $T$
		\FOR {$i = 1$ to $len(C)$}
			\FOR {$j = 1$ to $N$}
				\IF {($C_i == E_j$)}
					\STATE $T_j = Thread(C_i, V_1...V_M, (unassigned) E_1...E_N)$
				\ENDIF
			\ENDFOR
		\ENDFOR
		\RETURN $T$
	\end{algorithmic}
\end{algorithm}

The process in VRP solver procedure in each thread will produce at least $1$ route and at most $M$ routes. Every route $R_i$ that is produced will be published with topic $C_i$. After being published, the message broker will inform the publisher about the number of subscribers that receive the message. The identity of the subscribers that receive the message will remain unknown to the publisher.

If a route $R_i$ has more than one message receiver, the thread with ID $C_{R_i}$ will be cancelled. This annulment is aimed to prevent a solution/route that has been received by subscribers from being recomputed. There is a condition when the running VRP solver with ID $C_i$ does not produce the solution for topic $C_i$. In this kind of situation, the topic $C_i$ will be requeued with only including the subscriber as the enumerator. By doing this, there is a guarantee that the topic $C_i$  will obtain a solution/route.

\begin{algorithm}[h]
	\caption{VRPWorker}
	\label{alg:vrp-worker}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE $T$
		\ENSURE  $R$
		\FOR {$i = 1$ to $len(T)$}
			\STATE $R$ = VRPSolver($T_i$)
			\FOR {$j = 1$ to $len(R)$}
				\STATE $r$ = publish($C_{R_j}$, $R_j$)
				\IF {($r > 0$)}
					\STATE cancelSolver($T_j$)
				\ELSIF {($C_{T_i} \notin C_{R_j}$)}
					\STATE $T_i = Thread(C_{T_i}, V_m, (unassigned) E_1...E_N)$
				\ENDIF
			\ENDFOR
		\ENDFOR
		\RETURN $R$
	\end{algorithmic}
\end{algorithm}

As mentioned before, the advantage of using publish/subscribe mechanism is its loose coupling characteristic that makes it flexible. But this benefit could also be deemed as a shortcoming. The publisher's unawareness towards subscribers' identities has caused the current location of all subscribers cannot be identified. Hence, we need a mechanism that can support information exchanging between publisher and subscribers. The idea is to use a shared memory contains the current location data of all subscribers. By accessing this shared memory, the publisher will be able to determine the subscribers' current locations.

The process above will keep repeating until all enumeration locations have been assigned to the subscribers (enumerators). \autoref{fig:publisher-algorithm} illustrates the workflow of the algorithm used in recommendation publisher.

\begin{figure}[h]
	\centering
	\includegraphics[width=8cm]{Resources/Images/publisher-algorithm}
	\caption{Publisher Workflow}
	\label{fig:publisher-algorithm}
\end{figure}

%-----------------------------------------------------------------------------%
\subsection{VRP Solver}
\label{ssec:vrp-solver}
%-----------------------------------------------------------------------------%
VRP solver is a module used for finding a solution or route that will be visited. VRP solver is called in each thread in the thread pool (\autoref{alg:vrp-worker}). There are several algorithms that can be used in finding a solution in a MDVRP problem such as tabu search \cite{cordeau_tabu_1997}, adaptive large neighborhood search  \cite{pisinger_general_2007}, fuzzy logic guided genetic algorithm \cite{lau_application_2010}, paralel iterated tabu search \cite{cordeau_parallel_2012}, hybrid algorithm combining iterated local search and set partitioning \cite{subramanian_hybrid_2013}, hybrid genetic algorithm with adaptive diversity control \cite{vidal_implicit_2014}, hybrid granular tabu search \cite{escobar_hybrid_2014}, and cooperative coevolution algorithms (CoEAs) \cite{de_oliveira_cooperative_2016}. In this research, we will use coevolutionary algorithms (CoEAs) since CoEAs generates a competitive \textit{mean solution values} with relatively low CPU time compared to other algorithms \cite{de_oliveira_cooperative_2016}.

The steps that are used in VRP solver that adopts CoEAs algorithm are as follows:
\begin{enumerate}
	\item Create problem \\
	MDVRP problem that is designed consists of a number of vehicles $V$ and edges $E$ that are assigned to each thread. 
	\item Decompose problem \\
	MDVRP problem is decomposed into several subproblems. 
	\item Evolve. \\
	Each individual in every subproblem will be evolved. At the end of every evolution, new indivuals will be evaluated. If the new generated individuals are better than the previous ones, the solution is accepted and the best individuals will be updated. The evolution will keep happening until it reach the time limit of 60 seconds, or 40 seconds without any changes on the best individuals. 
\end{enumerate}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Field data collection is one of the main activities performed by the national statistical agencies in every country. Data collection activities have a similar workflow with Multi-Depot Vehicle Routing Problem (MDVRP). The use of MDVRP to generate pre-calculated routes resulted in total route costs with high standard deviation. The real-time mechanism by utilizing the publish/subscribe paradigm combined with Cooperative Coevolution Algorithms (CoEAs) is proposed to reduce the inequality (large variation) of the completion time. The test results show that routes produced by the combination of publish/subscribe paradigm and CoEAs are more prevalent in total route times among enumerators compared with the pre-calculated routes produced by CoEAs only.
\end{abstract}

@@

%-----------------------------------------------------------------------------%
\section{Introduction}
\label{sec:introduction}
%-----------------------------------------------------------------------------%
Data collection is one of the main duties of a statistical agency in every country. There are two data collection methods that are generally used: primary and secondary data collection. The primary data collection requires a direct interview with the respondents, while the secondary data collection only compiles the data collected by other agencies. Related to this, the primary data collection involves an activity of allocating the enumerators into several census/survey areas. The allocation is usually conducted by assigning an equal number of locations on each enumerator.

The workflow of the data collection performs as follows: 
\begin{enumerate}
	\item Each enumerator gets a list of census/survey locations to visit. 
	\item The enumeration starts on one particular point. It could be the statistical office or the enumerator's house. 
	\item The enumerator moves to the first census/survey location and visits all respondents in that location. 
	\item After finishing the first census/survey area, the enumerator moves to the second census/survey location and continue doing so until all locations have been visited successfully.
\end{enumerate}
This workflow is significantly similar to the Vehicle Routing Problem (VRP), specifically, the Multi-Depot Vehicle Routing Problem (MDVRP). The enumerators are analogous to vehicles, census/survey locations are comparable with customers, and the enumeration's starting point is corresponding with the depot.

However, although sharing similar workflow with MDVRP, the rough implementation of the MDVRP algorithm is not feasible for solving the allocation problems. This is because MDVRP needs the variable \textit{service time}, which will not be available until after the enumerator finishes visiting the census/survey location. Therefore, this research aims to propose an integration of MDVRP with publish/subscribe mechanism to create a real-time location recommendation system for field data collection.

%-----------------------------------------------------------------------------%
\section{Related Works}
\label{sec:related-works}
%-----------------------------------------------------------------------------%
%-----------------------------------------------------------------------------%
\subsection{Multi-Depot Vehicle Routing Problem (MDVRP)}
\label{ssec:mdvrp}
%-----------------------------------------------------------------------------%
VRP is an optimization problem that focused on the query: \textit{`given a set of vehicles and a starting point (depot), find the best route to visit all customers'}. In cases there is more than one depot, VRP is known as MDVRP \cite{montoya-torres_literature_2015}. \autoref{fig:mdvrp-illustration} shows an example of an MDVRP solution that uses two depots and two routes that associate with each depot. Basically, a solution for MDVRP is a set of routes such that: (i) each route starts and ends at the same depot, (ii) each customer is only served once by one vehicle, (iii) the total demand on each route does not exceed vehicle's capacity, (iv) the maximum route time is satisfied, and (v) the total cost is minimized.

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/mdvrp-illustration}
	\caption{An illustration for \textit{Multi Depot} VRP}
	\label{fig:mdvrp-illustration}
\end{figure}

According to Renaud et al \cite{renaud_tabu_1996}, the MDVRP can be formally described as follows:
\begin{enumerate}
	\item Let $G = (V, A)$ be a complete graph, where $V$ is the set of nodes and $A$ is the set of arcs. 
	\item Partition the nodes into two subsets: the customers to serve $V_C$ = \{1,..., $N$\} and the depots $V_D$ = \{$N$+1,..., $N+M$\}, with $V_C \cup V_D$ = $V$ and $V_C \cap V_D$ = $\oslash$. 
	\item There is a non-negative cost $c_{ij}$ associated with each arc $(i, j) \in A$. 
	\item The demand of each customer is $d_i$ (there is no demand at the depot nodes).
	\item There is also a fleet of $K$ identical vehicles, each with capacity $Q$.
	\item The service time at each customer $i$ is $t_i$ while the maximum route duration time is set to $T$.
	\item A conversion factor $w_{ij}$ might be needed to transform the cost $c_{ij}$ into time units. In the classical MDVRP, however, the cost is similar with the time and distance units. Hence, $w_{ij}$ = $1$.
\end{enumerate}

%-----------------------------------------------------------------------------%
\subsection{Evolution Algorithms (EAs)}
\label{ssec:evolution-algorithms}
%-----------------------------------------------------------------------------%
Evolution Algorithms (EAs) is an optimization algorithm inspired by nature. EAs involve selection and reproduction processes to purify population from the solution candidates. According to Engelbrecht \cite{engelbrecht_coevolution_2007}, the EAs lifecycle begins with randomly configuring the initial population. For each iteration, every individual in the population is evaluated using an objective function to find the solution candidates. Each solution candidate is labeled with a fitness value based on its evaluation result. These candidates will then reproduce and create the next generation. The whole process will be repeated using the new-generation individuals. The iteration will stop once it hits a certain time limit, which is 60 seconds.

In standard EAs, evolution is usually viewed as the population's attempts to adapt in a fixed physical environment. Furthermore, Coevolutionary algorithms (CoEAs), a development of EAs, realize that in natural evolution the physical environment is influenced by other independently-acting biological populations \cite{engelbrecht_coevolution_2007}. Based on the interaction of each species, CoEAs can be distinguished into two categories: competitive and cooperative \cite{engelbrecht_coevolution_2007}. In the competitive coevolution, each individual competes with other individuals in the same group. Meanwhile, the cooperative coevolution has its species mutually interacted or, at least, not harming each other.

%-----------------------------------------------------------------------------%
\subsection{Publish/Subscribe Paradigm}
\label{ssec:pub-sub}
%-----------------------------------------------------------------------------%
The publish/subscribe interaction is a communication method between client and server, which involves subscribers as clients. The subscribers are the parties who have interests in a certain event or the pattern of an event. These subscribers will get a notification from the publisher about the event they are interested in \cite{eugster_many_2003}.

The basic model of the publish/subscribe system, as can be seen in \autoref{fig:pub-sub-general}, depends on the event notification service that provides storage and management of subscription. This event service acts as a mediator between the publisher (the event's producer) and the subscriber (the event's consumer).

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/pub-sub-general}
	\caption{Basic architecture in Publish/Subscribe Mechanism \cite{eugster_many_2003}}
	\label{fig:pub-sub-general}
\end{figure}

One of the benefits of using publish/subscribe mechanism is the loose coupling characteristic \cite{eugster_many_2003} between the publisher and the subscriber. The separation of information (decoupling) between publisher and subscriber can be divided into 3 (three) dimensions, which are:

\begin{enumerate}
	\item Space decoupling. \\
	During the interaction, publisher and subscriber do not need to know each other. The publisher sends an event and subscriber indirectly receives the event through the event service. The publisher does not hold any reference towards the subscriber and vice versa. 
	\item Time decoupling. \\
	The parties who are involved in the interactions do not have to interact in the same time. The publisher can send the event while in a disconnected state. Similarly, the subscriber can still receive the event, albeit disconnected. 
	\item Synchronizing decoupling. \\
	Publisher will not be blocked during the event producing. The subscriber can still obtain information despite, at the same time, working on other tasks. Publisher and subscriber are not in the main flow, hence not interacting synchronously. 
\end{enumerate}

%-----------------------------------------------------------------------------%
\section{Proposed Solution}
\label{sec:proposed-solution}
%-----------------------------------------------------------------------------%
The drawback of using MDVRP for location recommendation is the absence of time service data, which is very important for computing the recommendation. Thus, MDVRP needs to be integrated with a real-time mechanism such as Web Service, Remote Procedure Call (RPC), message passing, and publish/subscribe mechanism \cite{eugster_many_2003}.

In this research, the publish/subscribe mechanism is chosen because, in addition to its loose coupling characteristic, it is also suitable for an information-driven system \cite{muhl_large-scale_2002}. Loosing coupling allows the publish/subscribe mechanism to work asynchronously, meaning the request and the reply do not have to be processed in sequence. The publisher and subscriber can commit offline publishing and subscription, respectively.

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/system-overview}
	\caption{The outline of the proposed system}
	\label{fig:system-overview}
\end{figure}

\autoref{fig:system-overview} shows the system outline consists of 3 (three) main components: the publisher, the subscriber, and the message broker. The communication between publisher and subscriber is built upon their similarity in either event or topic. In this research, the subscriber's current location is chosen as the communication topic.

%-----------------------------------------------------------------------------%
\subsection{The Recommendation Publisher}
\label{ssec:recommendation-publisher}
%-----------------------------------------------------------------------------%
VRP solver is implemented on the publisher's side. The publisher uses subscriber's current location as a topic to find the best solution/route. This route will be published to the subscriber via the message broker. The message broker plays a role in forwarding the message from publisher to subscriber and vice versa. Afterward, a new thread (\autoref{alg:topic-watcher}) is prepared to periodically check if there is any new topic at message broker.

Every time a new topic emerges, a new thread will be created with that new topic used as an ID. Each thread contains VRP solver procedure (\autoref{alg:vrp-worker}) that acts as a solution/route finder. Accordingly, a thread pool is provided to accommodate all threads from each topic arranged in arrival order. Since the topic is used as a thread ID, the thread pool size is equal to the number of census/survey location.

Each thread in the thread pool will be run consecutively, one session for each thread. Every running thread will find the solution by taking all $M$ vehicles and $(unassigned) N$ locations into account. This solution finding is performed using VRP solver procedure which is explained in more detail in \autoref{ssec:vrp-solver}.

\begin{algorithm}[!]
	\caption{TopicWatcher}
	\label{alg:topic-watcher}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE $C$
		\ENSURE  $T$
		\FOR {$i = 1$ to $len(C)$}
			\FOR {$j = 1$ to $N$}
				\IF {($C_i == E_j$)}
					\STATE $T_j = Thread(C_i, V_1...V_M, (unassigned) E_1...E_N)$
				\ENDIF
			\ENDFOR
		\ENDFOR
		\RETURN $T$
	\end{algorithmic}
\end{algorithm}

The VRP solver procedure in each thread will produce at least $1$ route and at most $M$ routes. Every route $R_i$ that is produced will be published with a topic $C_i$. The message broker will inform the publisher the number of subscribers that receive the message. The subscribers' identities will remain unknown to the publisher.

If a route $R_i$ has more than one message receiver, the thread with ID $C_{R_i}$ will be cancelled. This annulment is aimed to prevent a solution/route that has been received by subscribers from being recomputed. There could be a condition when the running VRP solver with ID $C_i$ does not produce the solution for topic $C_i$. In this situation, the topic $C_i$ will be requeued in thread pool by only involving the subscriber as the enumerator. As a result, there is a guarantee that every topic $C_i$ will have a solution/route.

\begin{algorithm}[!]
	\caption{VRPWorker}
	\label{alg:vrp-worker}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE $T$
		\ENSURE  $R$
		\FOR {$i = 1$ to $len(T)$}
			\STATE $R$ = VRPSolver($T_i$)
			\FOR {$j = 1$ to $len(R)$}
				\STATE $r$ = publish($C_{R_j}$, $R_j$)
				\IF {($r > 0$)}
					\STATE cancelSolver($T_j$)
				\ELSIF {($C_{T_i} \notin C_{R_j}$)}
					\STATE $T_i = Thread(C_{T_i}, V_m, (unassigned) E_1...E_N)$
				\ENDIF
			\ENDFOR
		\ENDFOR
		\RETURN $R$
	\end{algorithmic}
\end{algorithm}

Despite the flexibility, the loose coupling characteristics also brings a shortcoming to publish/subscribe mechanism. The publisher's unawareness towards subscribers' identities caused the subscribers' location cannot be identified. Hence, a mechanism that can support information exchange between publisher and subscribers is needed. The idea is to use a shared memory contains subscribers' current location data that can be accessed by the publisher.

The whole processes described above, from detecting a new topic to obtaining the solution, will keep repeating until all customers are already assigned to each vehicle. In terms of data collection, the entire iterative processes will stop once all census/survey locations have been assigned to each enumerator. \autoref{fig:publisher-algorithm} illustrates the workflow of the algorithm used in recommendation publisher.

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/publisher-algorithm}
	\caption{Publisher Workflow}
	\label{fig:publisher-algorithm}
\end{figure}

%-----------------------------------------------------------------------------%
\subsection{VRP Solver}
\label{ssec:vrp-solver}
%-----------------------------------------------------------------------------%
VRP solver is a module used for finding the best route/solution to visit all customers (census/survey locations) in a VRP/MDVRP. VRP solver is called in each thread in the thread pool (\autoref{alg:vrp-worker}). There are several algorithms that can be adopted to find the solution such as tabu search \cite{cordeau_tabu_1997}, adaptive large neighborhood search  \cite{pisinger_general_2007}, fuzzy logic guided genetic algorithm \cite{lau_application_2010}, paralel iterated tabu search \cite{cordeau_parallel_2012}, hybrid algorithm combining iterated local search and set partitioning \cite{subramanian_hybrid_2013}, hybrid genetic algorithm with adaptive diversity control \cite{vidal_implicit_2014}, hybrid granular tabu search \cite{escobar_hybrid_2014}, and cooperative coevolution algorithms (CoEAs) \cite{de_oliveira_cooperative_2016}. In this research, VRP solver utilizes CoEAs since CoEAs generates a competitive \textit{mean solution values} with relatively low CPU time compared to other algorithms \cite{de_oliveira_cooperative_2016}.

The VRP solver works as follows:
\begin{enumerate}
	\item Problem creation \\
	Create an instance of MDVRP that consists of $M$ vehicles (enumerators) and $N$ customers (locations).
	\item Problem decomposition \\
	Decompose the MDVRP into several subproblems using Nearest Insertion Heuristic (NIH) and Semi-greedy algorithm. Both of these algorithms are parts of CoEAs. 
	\item Individual evolution. \\
	Before each evolution, each individual in every subproblem is evaluated to find the current best individual (CBI) of all subproblems. Then, evolve each individual to generate new individuals. Evaluates these new individuals to find the new best individual (NBI). If NBI is better than CBI, update CBI with NBI value. Otherwise, leave the CBI as it is. Repeat the evolution process until it reaches the time limit of 60 seconds or 40 seconds if there is no change happens to the CBI.    
\end{enumerate}

\begin{algorithm}[!]
	\caption{VRPSolver}
	\label{alg:vrp-solver}
	\begin{algorithmic}[1]
		\renewcommand{\algorithmicrequire}{\textbf{Input:}}
		\renewcommand{\algorithmicensure}{\textbf{Output:}}
		\REQUIRE $T_i$
		\ENSURE  $R$
		\STATE P $\leftarrow$ createProblem($V_1...V_{T_i}$, $E_1...E_{T_i}$)
		\\ \textit{Decompose problem into S subproblem}
		\STATE SP $\leftarrow$ decomposeProblem(P)
		\WHILE {stopCriteriaUnmet}
			\FOR {$i=1$ to $len(SP)$}
				\STATE I $\leftarrow$ $SP_i \rightarrow individuals$
				\FOR {$j$ to $len(I)$}
					%\\ \textit{Foreach individu in subpopulation, do evolve}
					\STATE $O_j$ $\leftarrow$ $I_j \rightarrow evolve()$
				\ENDFOR
				\STATE shrink($I$, $O$)
			\ENDFOR
			%\\ \textit{Every iteration, update best individuals}
			\STATE updateBestIndividuals()
		\ENDWHILE
		\STATE $B \leftarrow getBestIndividuals()$ 
		\STATE $R \leftarrow convert(B)$ 
		\RETURN $R$
	\end{algorithmic}
\end{algorithm}

%-----------------------------------------------------------------------------%
\subsection{Message Broker}
\label{ssec:message-broker}
%-----------------------------------------------------------------------------%
A message broker is a component responsible for routing the message from publisher to subscriber based on the subscribed topic \cite{banavar_efficient_1999}. A publish/subscribe system can have a single broker or multi-broker. In single broker architecture, all subscribers and publishers are connected to one single broker, while in multi-broker architecture, every subscriber or publisher can connect to any nearest broker. This multi-broker architecture is also called distributed publish/subscribe system \cite{muhl_large-scale_2002} as depicted in \autoref{fig:pub_sub_distributed_ilustration}. In this research, the proposed design will implement distributed architecture since the census/survey locations are geographically scattered.

\begin{figure}[!]
	\centering
	\includegraphics[width=7cm]{Resources/Images/pub_sub_distributed_ilustration}
	\caption{The architecture of distributed publish-subscribe}
	\label{fig:pub_sub_distributed_ilustration}
\end{figure}

%-----------------------------------------------------------------------------%
\section{Result}
\label{sec:testing}
%-----------------------------------------------------------------------------%
The performance of the proposed system is assessed through a number of experiments. This experiment uses 2 (two) input data: Cordeau's data and real administrative data. The service time for these two data is randomly generated by following the normal distribution.

\begin{enumerate}
	\item The Cordeau's data \cite{cordeau_tabu_1997}, which consists of 50 customers (locations) and 4 vehicles (enumerators). The distances between locations are computed using euclidean formula. 
	\item The real administrative data, which consists of 182 customers (locations) and 15 vehicles (enumerators). The distances and the time needed to travel between locations are measured using Google Maps Direction API \cite{google_google_2016}. 
\end{enumerate}

\begin{figure}[!]
	\centering
	\includegraphics[width=8cm]{Resources/Images/client-algorithm-nornal-global}
	\caption{The flowchart of experiment scenario}
	\label{fig:client-algorithm-nornal-global}
\end{figure}
